%-------------------------
% Resume in Latex
% Author : Esteban Romo Esparza
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------

\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\resumeItemHeading}[2]{
  \vspace{4pt}\item\small{
    {\textbf{#1}: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSimpleSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Esteban Romo} \\ \vspace{1pt}
    \href{https://github.com/es-romo}{\underline{github.com/es-romo}} $|$ 
    \href{mailto:es-romo@proton.me}{\underline{es-romo@proton.me}} $|$ 
    \href{https://www.linkedin.com/in/es-romo/}{\underline{linkedin.com/in/es-romo}} $|$ 
    \small +1-437-344-0898
\end{center}

%-----------SKILLS-----------
\begin{minipage}[t]{.78\textwidth}
  \section{Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
      \small{\item{
      % \textbf{Languages}{: Typescript, SQL, Postgres, JavaScript, HTML, CSS.} \\
      \textbf{Languages}{: Typescript, C++, SQL, Postgres, JavaScript, HTML, CSS.} \\
      \textbf{Frameworks}{: React, React Native, Express, Fastify, Jest.} \\
      \textbf{Tools}{: Git, CircleCI, GitHub Actions, Jenkins, XCode, Lerna.} \\
      \textbf{Infrastructure}{: AWS, Elastic Beanstalk, RDS, ElastiCache, EC2, Terraform.} \\
      % \textbf{Libraries \& Others}{: Node.js, Typeorm, Ant Design, Tailwind, Redis, Docker, HL7.} \\
      \textbf{Libraries \& Others}{: Node.js, OpenGL, Dear ImGui, Ant Design, Tailwind, Redis, Docker.} \\
      }}
  \end{itemize}
\end{minipage}\hspace{.02\textwidth}%
 %-----------Languages-----------
\begin{minipage}[t]{.20\textwidth}
  \section{Languages}
  \begin{itemize}[leftmargin=0.0in, label={}]
      \small{\item{
      \textbf{English}{: Proficient} \\
      \textbf{Spanish}{: Native} \\
      }}
  \end{itemize}
\end{minipage}\vspace{-10pt}

%-----------WORK EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Full Stack Software Engineer}{Apr 2021 -- Nov 2023}
      {CANImmunize}{Remote}
      \resumeItemListStart
        \vspace{4pt}\resumeItem{Spearheaded the creation of multiple health-tech solutions across all stages of development.}
        \vspace{-4pt}\resumeItemHeading{VaxRecordNS}{Allows the residents of Nova Scotia to access their vaccination records.}
        \resumeItemListStart
          \resumeItem{Collaborated closely with multiple vendors as part of a wide effort to centralize the province's health data.}
          \resumeItem{Developed web and mobile apps using React, React Native, and Typescript that interface with a governmental OIDC provider and a FHIR data repository that stores the vaccination records of 1M+ patients.}
          \resumeItem{Designed scalable serverless services that allow users to manage their dependents and generate official their vaccination records using AWS Lambda, Twilio, and Redis.}
          \resumeItem{Created dashboards and alerts to monitor the health of the service with CloudWatch and Slack integrations.}
          \resumeItem{Set up CI/CD pipelines to build and deploy the applications with CircleCI.}
          \resumeItem{Managed the project's infrastructure using Terraform.}
        \resumeItemListEnd
        \resumeItemHeading{Shield}{Digital tool to help employers collect, manage and verify proof of vaccination of their employees.}
        \resumeItemListStart
          \resumeItem{Developed a SaaS product with Typescript, React, and PostgreSQL that handled PHI of up to 150K+ employees of major governmental and private organizations.}
          \resumeItem{Conducted interviews, assisted in hiring, and onboarded co-op students.}
          \resumeItem{Conducted code reviews of peers and mentored junior developers.}
          \resumeItem{Implemented suggestions from external cybersecurity audits to become SOC 2 compliant.}
        \resumeItemListEnd
        \resumeItemHeading{ClinicFlow}{End-to-end software solution for institutions to run paperless mass immunization campaigns.}
        \resumeItemListStart
          \resumeItem{Developed performant web, Android and iOS applications with React, React Native, and PostgreSQL that handle the forecasting, booking, and proof of vaccination of 1M+ Canadians.}
          \resumeItem{Headed deployments that involved major data migrations and infrastructure changes.}
          \resumeItem{Diagnosed, mitigated and solved critical incidents as the on-call engineer.}
        \resumeItemListEnd
      \resumeItemListEnd
    \resumeSubheading
      {Freelance Lead Developer}{Feb 2020 -- May 2020}
      {ppeburnrate.com}{Oakville, Ontario}
      \resumeItemListStart
        \resumeItem{Recruited and led a team of 5 developers in building a responsive web app that helps organizations manage their PPE consumption using React, Express, DigitalOcean and Microsoft SQL Server.}
      \resumeItemListEnd
    % \resumeSubheading
    %   {Shipping \& Receiving Associate}{Apr 2019 -- Sep 2020}
    %   {Areion International}{Oakville, Ontario}
    % \resumeSubheading
    %   {Inventory Administration Associate}{Jul 2018 -- Aug 2019}
    %   {Fenyw}{Guadalajara, Mexico}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sheridan College}{Sep 2019 -- Dec 2020}
      {Ontario College Diploma in Software Engineering}{Oakville, Ontario}
      \resumeItemListStart
        \resumeItem{Cumulative GPA: 3.93/4.00; High Honours.}
      \resumeItemListEnd
    % \resumeSubheading
    %   {The Web Developer Bootcamp}{Jun 2019 -- Aug 2019}
    %   {Online Certificate}{udemy.com}
    \resumeSubheading
      {Centro de Enseñanza Técnica Industrial}{Aug 2015 -- Jun 2019}
      {Technologist in Software Development}{Guadalajara, Mexico}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{@es-romo/coco} $|$ \emph{C++, OpenGL, Dear ImGui, assimp, emscripten }}{Feb 2024 -- Present}
          \resumeItemListStart
            \resumeItem{OpenGL 3D graphics engine for gLTF and OBJ files.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{@es-romo/relay} $|$ \emph{Typescript, Fastify, Lerna, Jest, GitHub Actions, Glitch }}{Nov 2023 -- Present}
          \resumeItemListStart
            \resumeItem{WebSocket relay server that bridges the communication between clients for use in listen server architectures.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
% \section{Volunteering}
% \resumeSubHeadingListStart
% \resumeSubheading
%   {Administration \& Events Staff}{2017}
%   {CODE Jalisco}{Guadalajara, Mexico}
% \resumeSubHeadingListEnd

%-----------PROJECTS-----------
% \section{Courses \& Events}
% \resumeSubHeadingListStart
%   \resumeSimpleSubheading
%   {Hack the Northeast: Beyond 2020}{Jan 2021}
%   \resumeSimpleSubheading
%   {HackUMBC 2020}{Nov 2020}
% \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
